Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-07-11 manuscript/manuscript.Rmd
Fiddling with the attributions again for mSystems formatting

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author: "William Kumler, Wei Qin, Rachel A. Lundeen, Benedetto Barone, Laura T. Carlson, and Anitra E. Ingalls"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---

>>>>

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler,$^a$ Wei Qin,$^{a*}$ Rachel A. Lundeen,$^a$ Benedetto Barone,$^b$ Laura T. Carlson,$^a$ Anitra E. Ingalls$^a$#
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---

$^a$School of Oceanography, University of Washington, Seattle, WA, USA

$^b$Daniel K. Inouye Center for Microbial Oceanography: Research and Education and Department of Oceanography, University of Hawai'i at Mānoa, Honolulu, HI, USA

Running head: Metabolites reflect variability introduced by eddies

\#Address correspondence to Anitra E. Ingalls, aingalls\@uw.edu

\*Present Address: School of Biological Sciences, Institute for Environmental Genomics, University of Oklahoma, Norman, OK, USA

Word counts:

  - Abstract: 216
  - Importance: 123
  - Main text (excluding Methods, figure captions, references, etc.): 5453
